Geographical Python Teaching Resources: GeoPyTeR

### 2019-10-19 Geopyter.tex
submission to jgs

\documentclass[letter, 11pt]{article}

@@

\title{Geographical Python Teaching Resources: GeoPyTeR}
\author{Jonathan Reades \and Sergio Rey}

@@

\begin{abstract}
  Abstract goes here.
\end{abstract}

>>>>

\documentclass[letter, 11pt,titlepage]{article}

@@

\title{Geographical Python Teaching Resources: GeoPyTeR}
\author{Jonathan Reades \and Sergio J. Rey}
%\author{}

@@

\begin{abstract}
Geopyter, an acronym of Geographical Python Teaching Resources, provides
a hub for the distribution of `best practice' in computational and
spatial analytic instruction; enabling instructors to quickly and
flexibly remix contributed content to suit their needs and delivery
framework; and encouraging contributors from around the world to `give
back' whether in terms of how to teach individual concepts or deliver
whole courses. As such, Geopyter is positioned at the confluence of two
powerful streams of thought in software and education: the Free and Open
Source Software (FOSS) movement in which contributors help to build
better software, usually on an unpaid basis, in return for having access
to better tools and the recognition of their peers); and the rise of
Massive Open Online Courses (MOOCs), which seek to radically expand
access to education by moving course content online and providing access
to students anywhere in the world at little or no cost. This paper sets
out in greater detail the origins and inspiration for Geopyter, the
design of the system and, through examples, the types of innovative
workflows that it enables for teachers. We believe that tools like
Geopyter, which build on open teaching practices and promote the
development of a shared understanding of what it is to \emph{be} a
computational geographer represent an opportunity to expand the impact
of this second wave of innovation in instruction while reducing the
demands placed on those actively teaching in this area.
\end{abstract}
